---
title: "607 Homework 1"
author: "Dariusz Siergiejuk"
date: "9/1/2020"
output: html_document
---

# Load Libraries

```{r}
library(ggplot2)
library(stats)
library(devtools)
library(RCurl)
```

```{r}
library(plyr)
```

# Import file as CVS, check variables.

## Data File comes with a header row so we must indicate "header=T".

```{r}
x <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/librarians/librarians-by-msa.csv")
y<-data.frame(read.csv(text=x, header=T))
dim(y)
```


```{r}
head(y)
```

# Rename Column Headers

```{r}
head(rename(y,c("prim_state"="State","area_name"="Area","tot_emp"="Employee Count","emp_prse"="Present","jobs_1000"="Jobs","loc_quotient"="Quotient")))
```

# Select a subset by row.

## How many wood libraries are over the present?

```{r}
LibrariesPresent <- subset(y, prim_state <80 & emp_prse=="Present")
LibrariesPresent
```


```{r}
summary(LibrariesPresent)
```

## How many libraries are over the present?

```{r}
LibrariesPresent <- subset(y, prim_state <10 & emp_prse=="Present")
LibrariesPresent
```

```{r}
summary(LibrariesPresent)
```

# Select a subset by column and row.

## Show select information for new/old libraries.

```{r}
LibrariesNew<-subset(y,prim_state>1.61,select=c(area_name,tot_emp,jobs_1000,loc_quotient))
LibrariesNew
```

```{r}
summary(LibrariesNew)
```

# Bar Plot

## What's the quotient by state?

```{r}
barplot(table(y$loc_quotient), ylim=c(1,5.00),main="Quotient by State")
```

End of File














