---
title: "Assignment Three"
author: "Dariusz Siergiejuk"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: hpstr
    highlight: github
# Possible pretty doc themes are:
#     cayman, architect, tactile, hpstr, leonids
---

### Assignment Goal

In prior assignments we scrutinized data sets that came in table format. The goal of assignment at hand is to make use of regular expressions and all-important string functions for inspecting data that are not readily available in the form of elegantly organized data sets yet in ordinary text.

Please deliver links to an R Markdown file (in GitHub and rpubs.com) with solutions to the problems below.
You may work in a small group, but please submit separately with names of all group participants in your submission.

### 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/],provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r}
library(readr)
library(RCurl)
library(tidyverse)

x <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv")
majors <- read.csv(text=x)

majors_data <- data.frame(majors)
stats_data_majors <- subset(majors_data, grepl("DATA", Major) | grepl("STATISTICS", Major))

stats_data_majors
```

### 2. Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"

[9] "elderberry"   "lime"         "lychee"       "mulberry"

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili
pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
(exotic_fruits <-c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry"))
```

```{r}
(new_fruit <- glue::glue('c("{fruitlist}")',
  fruitlist = glue::glue_collapse(exotic_fruits, sep = '", "')))
```

The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:

### 3. Describe, in words, what these expressions will match:

  * (.)\1\1
  * "(.)(.)\\2\\1"
  * (..)\1
  * "(.).\\1.\\1"
  * "(.)(.)(.).*\\3\\2\\1"

```{r}
# * `(.)\1\1`: The same character showing up three times in a row.
```

#### Clarification

 * (.) Capturing Group
 * . matches any character (with the exception of line terminators)
 * \1 matches the same text as most recently matched by the 1st capturing group
 * \1 matches the same text as most recently matched by the 1st capturing group

```{r}
# * `"(.)(.)\\2\\1"`: A pair of characters followed by the same pair of characters in reversed order.
```

#### Clarification

 * (.) 1st Capturing Group
 * . matches any character (with the exception of line terminators)
 * (.) 2nd Capturing Group
 * . matches any character (with the exception of line terminators)
 * \ matches the character word for word
 * 2 matches the character 2 word for word
 * \ matches the character word for word (case sensitive)
 
```{r}
 # * `(..)\1`: Any two characters repeated.
```
 
#### Clarification

 * (..) Capturing Group
 * . matches any character (with the exception  of line terminators)
 * . matches any character (with the exception  of line terminators)
 * \1 matches the same text as most recently matched by the 1st

```{r}
# * `"(.).\\1.\\1"`: Character followed by any character, the original character, any other character, the original character again.
```

#### Clarification

 * (.) Capturing Group
 * . matches any character (with the exception of line terminators)
 * . matches any character (with the exception of line terminators)
 * \ matches the character  word for word (case sensitive)
 * 1 matches the character 1 word for word (case sensitive)
 * . matches any character (with the exception of line terminators)
 * \ matches the character  word for word (case sensitive)

```{r}
# * `"(.)(.)(.).*\\3\\2\\1"` Three characters followed by zero or more characters of any kind followed by the same three characters but in reverse order.
```

#### Clarification

 * 1st Capturing Group (.)
 * . matches any character (with the exception of line terminators)
 * 2nd Capturing Group (.)
 * . matches any character (with the exception of line terminators)
 * 3rd Capturing Group (.)
 * . matches any character (with the exception of line terminators)
 * .* matches any character (with the exception of line terminators)
 * Quantifier — Matches between zero and unlimited times, as many times as possible, giving back as needed (greedy)
 * \ matches the character  word for word
 * 3 matches the character 3 word for word
 * \ matches the character  word for word
 * 2 matches the character 2 word for word
 * \ matches the character word for word

### 4. Construct regular expressions to match words that:

  * Start and end with the same character.
  
```{r}
str_bring <- function(string, pattern) {
  string[str_detect(string, pattern)]
}
```

```{r}
str_bring(words, "^(.).*\\1$")
```

  * Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
  
```{r}
str_bring(words, "(..).*\\1")
```
  
  
  * Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
  
```{r}
str_bring(words, "([a-z]).*\\1.*\\1")
```


### Synopsis

Regular expressions come handy since we are quite often forced to deal with strings containing unstructured and semi-unstructured data, for that regexps feature some concise langauge application in regard to various patterns showing up in strings.


Thank you, note this is the end of the file.